### 2019-12-22 article.tex
discussion improved

\begin{figure*}
	\includegraphics[width=0.8\linewidth]{images/3dCnn}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure*}

@@

>>>>

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.8\linewidth]{images/3dCnn}
	\end{center}
	\caption{3D CNN demonstration (kernel size = 3$\times$3$\times$3).}
	\label{fig:CnnSample}
\end{figure*}

@@

Figures \ref{fig:tests_1} to \ref{fig:tests_8} show different diagrams of loss and accuracy compared to normal CNNs. This behavior is the result of using dropouts which prevent gradient descent to smoothly decrease loss \cite{Gal2016}. These smooth steps can be seen in small parts of the diagram but not in the whole diagram. As we add dropout layers, gradient descent tries to minimize the loss of the training. As long as the dropout layers stay the same, everything works as expected. However, as the dropout layers vary, the loss changes dramatically and as a result, the loss diagram becomes noisy.

In conclusion, fMRI data contains a lot of both temporal and spatial information and we can take advantage of them if we find proper models. Our proposed method can classify patients based on spatial information only and does not use any kind of time based models or temporal data. Also, our research verifies that each fMRI time-slice contains enough information to diagnose diseases and is acceptably accurate.
